week getbackontrack

### 2024-11-03 1definedata.Rmd
defindedatapolsci

# install an old version of RSiena including sienaRI
# remove.packages("RSiena") #use this to remove the current version of RSiena
#devtools::install_version("RSiena", version = "1.3.14", repos = "http://cran.us.r-project.org") # This installs an older version

@@

@@

@@

fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

# before my edits:
# f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology", affiliation = "RU",
#     wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023)))

#after taking out discip = "sociology" in this first part    
f_pubnets <- function(df_scholars = df, list_publications = publications, affiliation = "RU",
    wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

@@

    networklist <- list()
    for (wave in 1:length(wave)) {
        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
    }

    publicationlist <- list()
    for (wave in 1:length(wave)) {
        publicationlist[[wave]] <- publications %>%
            filter(gs_id %in% df_sel$gs_id) %>%
            filter(year %in% wave[[wave]]) %>%
            select(author) %>%
            lapply(str_split, pattern = ",")
    }

    publicationlist2 <- list()
    for (wave in 1:length(wave)) {
        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
            # lowercase
        lapply(tolower) %>%
            # Removing diacritics
        lapply(stri_trans_general, id = "latin-ascii") %>%
            # only last name
        lapply(word, start = -1, sep = " ") %>%
            # only last last name
        lapply(word, start = -1, sep = "-")
    }

    for (wave in 1:length(wave)) {
        # let us remove all publications with only one author
        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
    }

    for (wave in 1:length(wave)) {
        pubs <- publicationlist2[[wave]]
        for (ego in 1:nrow(df_sel)) {
            # which ego?
            lastname_ego <- df_sel$lastname[ego]
            # for all publications
            for (pub in 1:length(pubs)) {
                # only continue if ego is author of pub
                if (lastname_ego %in% pubs[[pub]]) {
                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
                  # only continue if ego is first author of pub
                  if (aut_pot == 1) {
                    # check all alters/co-authors
                    for (alter in 1:nrow(df_sel)) {
                      # which alter
                      lastname_alter <- df_sel$lastname[alter]
                      if (lastname_alter %in% pubs[[pub]]) {
                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
                      }
                    }
                  }
                }
            }
        }
    }
    return(list(df = df_sel, network = networklist))
}
```

```{r}
view(f_pubnets)
```

@@

#prior to my edits:
# fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", wave = list(c(2019, 2023)), type = c("first"))

#after taking out discipline= "sociology" in the first part 
fcolnet <- function(data = scholars, university = "RU", wave = list(c(2019, 2023)), type = c("first")) {

@@

    # step 2
    ids <- demographics_soc$au_id
    nwave <- length(wave)
    nets <- array(0, dim = c(nwave, length(ids), length(ids)), dimnames = list(wave = 1:nwave, ids,
        ids))
    dimnames(nets)

@@

    # step 4
    if (type == "first") {
        for (j in 1:nwave) {
            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwave) {
            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwave) {
            df_works_w <- df_works[df_works$works_year >= wave[[j]][1] & df_works$works_year <= wave[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)

}

@@

## load data

```{r}
scholars <- fload("./data/processed/scholars_20240924.rda")

# save the output of your function

# before my edits:
# test <- fcolnet(data = scholars, university = "RU", discipline = "sociology", wave = list(c(2019, 2023)), type = c("first"))

# after taking discipline= "sociology" out
# test <- fcolnet(data = scholars, university = "RU", wave = list(c(2019, 2023)), type = c("first"))

# here is where the error occurs due to taking out the discipline = "sociology" in multiple prior parts of the code 
```

@@

```{r}
wave <- test$nets[1, , ]

# let us put the diagonal to zero
diag(wave) <- 0
# we want a binary tie (not a weighted tie)
wave[wave > 1] <- 1

# put the nets in an array
net_soc_array <- array(data = c(wave), dim = c(dim(wave), 2)) 
str(net_soc_array)  #now we basically restructured this 
# output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0

# since I only take one wave should I replace the 2 with a 1 here? 
net_soc_array1 <- array(data = c(wave), dim = c(dim(wave), 1)) 
str(net_soc_array1)  #now we basically restructured this 
# output: num [1:50, 1:50, 1] 0 0 0 0 0 0 0 0 0 0
```

@@

@@

```{r}
dim(test$nets)
```

@@

@@

# dependent 
 nets <- test$nets

df_ego_demo <- test$data$demographics
df_ego_oa <- test$data$scholars_oa
df_ego_works <- test$data$works

@@

# --> EGO DATAFRAME with demo and oa 
  ?join.data.frame
  df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

  rownames(nets[1,,]) == df_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

@@

@@

```{r}
df_ego$Naam # list of all names

df_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
                   0,1,1,0,1,0,1,1,1,1,
                   0,1,1,0,1,1,0,1,0,1,
                   0,1,0,0,0,0,0,0,1,0,
                   0,1,1,1,0,1,0,1,0,0) 
# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank

# check if it went smoothly 
view(df_ego[c('Naam', 'gender', 'au_id')])

@@

## H-index

Inspired by Lucan's code:

```{r}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

@@

>>>>

# install an old version of RSiena including sienaRI
#remove.packages("RSiena") #use this to remove the current version of RSiena
#devtools::install_version("RSiena", version = "1.3.14", repos = "C:/Users/Vero/OneDrive - Radboud Universiteit/Documents/GitHub/labjournal") # This installs an older version

@@

# require(RSiena)
# require(RsienaTwoStep)

@@

I do not seem to be able to call on the package RSiena, nor can I reinstall it.... I know programming never works on the first try but... goddamnit, why not even after 15?

@@

```{r}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

# this is the most important one. We created it in the previous script

f_pubnets <- function(df_scholars = df, list_publications = publications, discip = "sociology"+"political science", affiliation = "RU",
    waves = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

@@

    networklist <- list()
    for (wave in 1:length(waves)) {
        networklist[[wave]] <- matrix(0, nrow = nrow(df_sel), ncol = nrow(df_sel))
    }

    publicationlist <- list()
    for (wave in 1:length(waves)) {
        publicationlist[[wave]] <- publications %>%
            filter(gs_id %in% df_sel$gs_id) %>%
            filter(year %in% waves[[wave]]) %>%
            select(author) %>%
            lapply(str_split, pattern = ",")
    }

    publicationlist2 <- list()
    for (wave in 1:length(waves)) {
        publicationlist2[[wave]] <- publicationlist[[wave]]$author %>%
            # lowercase
        lapply(tolower) %>%
            # Removing diacritics
        lapply(stri_trans_general, id = "latin-ascii") %>%
            # only last name
        lapply(word, start = -1, sep = " ") %>%
            # only last last name
        lapply(word, start = -1, sep = "-")
    }

    for (wave in 1:length(waves)) {
        # let us remove all publications with only one author
        remove <- which(sapply(publicationlist2[[wave]], FUN = function(x) length(x) == 1) == TRUE)
        publicationlist2[[wave]] <- publicationlist2[[wave]][-remove]
    }

    for (wave in 1:length(waves)) {
        pubs <- publicationlist2[[wave]]
        for (ego in 1:nrow(df_sel)) {
            # which ego?
            lastname_ego <- df_sel$lastname[ego]
            # for all publications
            for (pub in 1:length(pubs)) {
                # only continue if ego is author of pub
                if (lastname_ego %in% pubs[[pub]]) {
                  aut_pot <- which.max(pubs[[pub]] %in% lastname_ego)
                  # only continue if ego is first author of pub
                  if (aut_pot == 1) {
                    # check all alters/co-authors
                    for (alter in 1:nrow(df_sel)) {
                      # which alter
                      lastname_alter <- df_sel$lastname[alter]
                      if (lastname_alter %in% pubs[[pub]]) {
                        networklist[[wave]][ego, alter] <- networklist[[wave]][ego, alter] + 1
                      }
                    }
                  }
                }
            }
        }
    }
    return(list(df = df_sel, network = networklist))
}

@@

```{r}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

    # step 2
    ids <- demographics_soc$au_id
    nwaves <- length(waves)
    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
        ids))
    dimnames(nets)

@@

    # step 4
    if (type == "first") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}

@@

## load and inspect data

```{r}
scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse

#inspecting scholars_20240924.rda object
#df_ego <- do.call(rbind.data.frame, scholars$demographics)
#unique(df_ego$discipline.22)

# save the output of your function
testsoc  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)),

                            type = c("first"))

# I DONT KNOW HOW TO MAKE ALL SCHOLARS BE PART OF SAME FUNCTION ("sociology"+ "political science" does not work...)

testpolsci <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "political science", 
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))
```

@@

## waves - sociology department

# Jochem messed up and did: waves, rows, columns [1, , ]
socwave1 <- testsoc$nets[ , ,1]  #rows, columns, waves
socwave2 <- testsoc$nets[ , ,2]  #rows, columns, waves
# let us put the diagonal to zero
diag(socwave1) <- 0
diag(socwave2) <- 0
# we want a binary tie (not a weighted tie)
socwave1[socwave1 > 1] <- 1
socwave2[socwave2 > 1] <- 1
# put the nets in an array
net_soc_array <- array(data = c(socwave1, socwave2), dim = c(dim(socwave1), 2))

str(net_soc_array)  #now we basically restructured this 
# output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0
```

## waves - polsci department

```{r}
# Jochem messed up and did: waves, rows, columns [1, , ]
polwave1 <- testpolsci$nets[ , ,1]  #rows, columns, waves
polwave2 <- testpolsci$nets[ , ,2]  #rows, columns, waves
# let us put the diagonal to zero
diag(polwave1) <- 0
diag(polwave2) <- 0
# we want a binary tie (not a weighted tie)
polwave1[polwave1 > 1] <- 1
polwave2[polwave2 > 1] <- 1
# put the nets in an array
net_pol_array <- array(data = c(polwave1, polwave2), dim = c(dim(polwave1), 2))

str(net_pol_array)  #now we basically restructured this

@@

### ANSWER:

RSiena needs at least two waves, because it models the evolution of the networks. We have to store the networks in an array before we can convert it to an dependent variable objects. Moreover, for RSiena the dimensions should be in the following order: rows, columns, waves.

I 'messed up' my function (for didactic reasons ;-) )and stored the nets in the following order: waves, rows, columns. Thus, either correct my function or retrieve the separate waves and store them in the order RSiena requires.

### QUESTION TO THE ANSWER:

We had agreed on me only investigating one time point for the sake of simplicity. It seems I basically have no choice but to investigate two waves, revisit my RQs and make an additional RQ about tie changes over time, right?

Then I would end up with 4 RQs and that seems like more than it needs to be for this project (great for a research incentive, but for this class I need to keep it simple, as I am currently very overworked).

Any advice on how I can keep it simple, nonetheless?

@@

```{r}
dim(testsoc$nets)
```

```{r}
dim(testpolsci$nets)
```

@@

### sociology dep.

@@

# dependent 
nets <- testsoc$nets

df_ego_demo <- testsoc$data$demographics
df_ego_oa <- testsoc$data$scholars_oa
df_ego_works <- testsoc$data$works

@@

  # --> EGO DATAFRAME with demo and oa (sociology)
  ?join.data.frame
  df_soc_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

  rownames(nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

@@

### polsci department

```{r}
# dependent
# pol_net <- sienaDependent(net_pol_array)

# dependent 
pol_nets <- testpolsci$nets

df_pol_ego_demo <- testpolsci$data$demographics
df_pol_ego_oa <- testpolsci$data$scholars_oa
df_pol_ego_works <- testpolsci$data$works

# DEMO
  str(df_pol_ego_demo, 1)

  df_pol_ego_demo <- do.call(rbind.data.frame, df_pol_ego_demo)
  df_pol_ego_demo[[1]]

# OA
  #str(df_pol_ego_oa, 1)
  df_pol_ego_oa[[1]]
  df_pol_ego_oa <- do.call(rbind.data.frame, df_pol_ego_oa)

# --> EGO DATAFRAME with demo and oa (political science)
  df_pol_ego <- left_join(df_pol_ego_demo, df_pol_ego_oa, by = join_by(au_id == id))

  rownames(pol_nets[1,,]) == df_pol_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!
```

@@

### gender-soc

```{r}
df_soc_ego$Naam # list of all names in sociology department

df_soc_ego$gender <- c(0,1,0,1,0,0,1,1,0,0,
                       0,1,1,0,1,0,1,1,1,1,
                       0,1,1,0,1,1,0,1,0,1,
                       0,1,0,0,0,0,0,0,1,0,
                       0,1,1,1,0,1,0,1,0,0) 
# manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank

# check if it went smoothly 
view(df_soc_ego[c('Naam', 'gender', 'au_id')])

### gender - polsci

```{r}
df_pol_ego$Naam # list of all names

df_pol_ego$gender <- c(1,0,1,0,0,0,1,0,1,0,
                       1,1,0,0,1,1,1,0,0,1,
                       0,1,1,0,0,1,1,1,0,0,
                       0,0,0,1,1,0,0,1,1,0,
                       0,0,0,1,0,1,1,1,0,0,0) 
    # manually filled in gender 0 = woman, 1 = man, based on majority given in NL voornamen bank, Guangyu was not in name bank but based on the employee-picture of RU, this person presents feminine, thus I assumed 0.

# check if it went smoothly 
view(df_pol_ego[c('Naam', 'gender', 'au_id')])

@@

### joining polsci and soc data

```{r}
df_both_ego <- full_join(df_soc_ego, df_pol_ego, by = join_by
                    (au_id == au_id, 
                     Naam==Naam, 
                     gender == gender, 
                     discipline.22 == discipline.22,
                     discipline.24 == discipline.24,
                     counts_by_year== counts_by_year, 
                     works_count == works_count, 
                     cited_by_count == cited_by_count, 
                     Universiteit1.22 == Universiteit1.22,
                     Universiteit2.22 == Universiteit2.22,
                     Universiteit1.24 == Universiteit1.24,
                     Universiteit2.24 == Universiteit2.24,
                     Universiteit.22 == Universiteit.22, 
                     Universiteit.24 == Universiteit.24,
                     no_oa_id == no_oa_id,
                     display_name == display_name,
                     display_name_alternatives == display_name_alternatives,
                     ids== ids,
                     orcid == orcid,
                     year.22 == year.22,
                     year.24 == year.24,
                     Functie.24== Functie.24,
                     relevance_score == relevance_score,
                     affiliation_display_name == affiliation_display_name,
                     affiliation_ror == affiliation_ror,
                     affiliation_id == affiliation_id,
                     affiliation_country_code == affiliation_country_code,
                     affiliation_type == affiliation_type,
                     affiliations_other == affiliations_other,
                     affiliation_lineage == affiliation_lineage,
                     Specialisatie.22 == Specialisatie.22,
                     Specialisatie.24 == Specialisatie.24,
                     x_concepts == x_concepts,
                     works_api_url == works_api_url))
# 101 scholars (50 sociology + 51 polsci) and 43 variables (as opposed to 21 bc i could not join them all.)

# GODDAMMIT WHY DO I ONLY FIND THIS NOW?!?!?!?!
# mydata <- sienaDataCreate(net, gender)
```

## QUESTION:

With 101 scholars, instead of the nr. of scholars of looking at just one department, I wonder if this is where we could simplify. Looking at a change over time, but not looking through a lens that wants to compare the two departments. Instead, I could just look at one department.

What do you think?

## H-index webscraping

Credits to Lucan for the code.

```{r}
# Add h-index and i10-index columns to df_ego
df_ego <- df_both_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

@@

## Actually define data:

```{r}
# dependent:
# net <- sienaDependent(net_soc_array)

#covariate 1
# gender <- coCovar(df_ego$gender)
# covariate 2
# h_index <- coCovar(df_ego$h_index)

#combining data: wish I knew of this shit earlier...
# mydata <- sienaDataCreate(net, gender)
```

# Create effects structure

```{r}
#myeff <- getEffects(mydata)
```

### 2024-11-03 weekbacktrack.Rmd
defindedatapolsci

+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+

@@

+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:=========================================================+

@@

| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking_meh.jpg){width="800"}Plotting                 | ![](images/timetopanic.gif){width="800"}[chores at home] |
|                                                                                               |                                                            | [Asked Jochem for input]                                      |                                                                                            | hyp. 3                                                          |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               | Outline Intro and theory [W]\                                                              |                                                                 | Revisit RQs [D]                                                           |                                                          |
|                                                                                               |                                                            |                                                               | (missing H3 still)                                                                         | Clarify [D]\                                                    |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               |                                                                                            | & define data [S1]\                                             |                                                                           |                                                          |
|                                                                                               |                                                            |                                                               |                                                                                            | & create effects structure [S2]                                 |                                                                           |                                                          |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+

@@

@@

|                                                                                               |                                                            |                                                               | Revisit RQs                                                                                |                                                                 |                                                                           |                                                          |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+----------------------------------------------------------+

>>>>

+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+

@@

+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:========================================================+

@@

| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/timetopanic.gif){width="800"}[chores at home, depression day]  | ![](images/socialnetworking_meh.jpg)Get polSci data,    |
|                                                                                               |                                                            | [Asked Jochem for input]                                      |                                                                                            | Clarify [D]\                                                    |                                                                           |                                                         |
|                                                                                               |                                                            |                                                               | OUTLINE Intro and theory [W]\                                                              | & define data [S1]\                                             |                                                                           | define data                                             |
|                                                                                               |                                                            |                                                               | (missing H3 still)                                                                         |                                                                 |                                                                           |                                                         |
|                                                                                               |                                                            |                                                               |                                                                                            | \* struggle with polsci data \*                                 |                                                                           |                                                         |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+

@@

| & create effects structure [S2]                                                               |                                                            |                                                               | Plotting & revisit RQs                                                                     | Revisit RQs                                                     |                                                                           |                                                         |

@@

| revisit RQs                                                                                   |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------+
